---
title: "Case Study Group_25"
author: "Jan Schulze, Jean Vincent Alexander Dunker, Tim Ferdinand Westhoff, Quoc Trung Luu"
date: "8/30/2021"
output: 
  html_document:
    toc: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE)
```

## Importing the data
All the necessary libraries and data from files needed is loaded in advance
```{r}
library(dplyr)
library(stringr)
library(readr)
vehicles_type11 <- read_csv("./Data/Fahrzeug/Fahrzeuge_OEM1_Typ11.csv")
bestandteile_vehicle11 <- read_csv2("./Data/Fahrzeug/Bestandteile_Fahrzeuge_OEM1_Typ11.csv")
komponentek1di1 <- read_csv("./Data/Komponente/Komponente_K1DI1.csv")
bestandteile_engine <- read_csv2("./Data/Komponente/Bestandteile_Komponente_K1DI1.csv")
txt_teil1 <-read_file("./Data/Einzelteil/Einzelteil_T01.txt")
txt_teil2 <-read_file("./Data/Einzelteil/Einzelteil_T02.txt")
t5 <- read_csv("./Data/Einzelteil/Einzelteil_T05.csv")
t6 <- read_csv("./Data/Einzelteil/Einzelteil_T06.csv")
zl <- read_csv2("./Data/Zulassungen/Zulassungen_alle_Fahrzeuge.csv")
geo_daten_gemeinden <- read_csv2("./Data/Geodaten/Geodaten_Gemeinden_v1.2_2017-08-22_TrR.csv")
```

## Data preparation 

Some side values are needed for the filtering of the data
```{r}
from_faulty <- as.Date("21.09.2010",format = "%d.%m.%Y")
to_faulty <- as.Date("04.09.2012", format = "%d.%m.%Y")
```
Get all IDs of vehicles type 11
```{r}
v11 <- vehicles_type11 %>% select(ID_Fahrzeug)
```
Engines of type 'K1DI1'
```{r}
b11 <- bestandteile_vehicle11 %>% filter(str_detect(ID_Motor, "K1DI1"))
```
Vehicles (v11) and eniges (b11) are connected with the attribute 'ID_Fahrzeug'
Inner join both tables. Remaining are only vehicles of type 11 with engine 'K1DI1'

Only the columns 'ID_Fahrzeug' and 'ID_Motor' are needed now
```{r}
v11_b11 <- v11 %>% inner_join(b11, by = "ID_Fahrzeug") %>% select(ID_Fahrzeug, ID_Motor)
```
Next all engines that are not produced within the specified time range are filtered out:
21.09.2010 (=from_faulty) to 04.09.2012 (=to_faulty)

Clean up Bestandteile k1di1
Work on entries with .x suffix: only take rows, where ID_Motor.x is not NA
Only take columns that are relevant for us and remove '.x' suffix from column name
Same procedure for '.y' and none suffix

At the end the objects are stacked and columns are renamed to make them distinguishable later on
```{r}
bmotor1 <- komponentek1di1 %>% filter(!is.na(ID_Motor.x)) %>%
  select(ID_Motor.x, Produktionsdatum.x, Fehlerhaft.x) %>% 
  rename_with(~str_remove(., '.x'))
bmotor2 <- komponentek1di1 %>% filter(!is.na(ID_Motor.y)) %>%
  select(ID_Motor.y, Produktionsdatum.y, Fehlerhaft.y) %>% 
  rename_with(~str_remove(., '.y'))
bmotor3 <- komponentek1di1 %>% filter(!is.na(ID_Motor)) %>%
  select(ID_Motor, Produktionsdatum, Fehlerhaft)
bmotor <- rbind(bmotor1, bmotor2, bmotor3)
bmotor <- bmotor %>% rename(Produktionsdatum.Motor = Produktionsdatum,
                            Fehlerhaft.Motor = Fehlerhaft)
```
bmotor_prod will contain engines of type k1di1 that were produced within the given time frame
```{r}
bmotor_prod <- bmotor %>% filter(Produktionsdatum.Motor >= from_faulty &
                                   Produktionsdatum.Motor <= to_faulty)
```
Inner join two tables (they are connected by 'ID_Motor')

This table will now have vehicles of type 11 with engine of type k1di1 that are
produced from 21.09.2010 to 04.09.2012
```{r}
v11_motor_date <- v11_b11 %>% inner_join(bmotor_prod, by="ID_Motor")
```
Inner join again with the table that shows the parts of engine k1di1
As result all vehicles of type 11 with engine of type k1di1 and all the components of its engine that are produced from 21.09.2010 to 04.09.2012 are shown

```{r}
kompo_date_motor <- bestandteile_engine %>% inner_join(v11_motor_date, by=c("ID_K1DI1"="ID_Motor"))
```
The single parts of the engine are now needed for further analysis. 
As shown in 'kompo_date_motor' Einzelteile T1, T2, T5 and T6 are needed.

The routine for Einzelteil T01 and T02 is the same.
Replace column separator " |  | " with ";".

```{r}
txt <- str_replace_all(txt_teil1, " \\| \\| ", ";")
rm(txt_teil1)
invisible(gc())
```
scan will read the values from `txt` into the vector `lines`. It will read 
characters and will create a entry in the vector after it encounters a single whitespace.
This way every element in the vector represents a row of the dataset.

```{r}
lines <- scan(textConnection(txt), what = "character", sep = " ")
rm(txt)
```
Split each element of the vector up by ";". 
```{r}
text <- str_split(lines, ";")
rm(lines)
invisible(gc())
```
The column names of the dataset are in the first element.
```{r}
col_names <- text[[1]]
```
Remove first column
```{r}
text <- purrr::map(text[2:length(text)], function(line) {line[-1]})
text <- unlist(text)
```
Convert the huge vector to a matrix...
```{r}
mat <- matrix(text, ncol = length(col_names), byrow = TRUE)
```
...and give its columns names
```{r}
colnames(mat) <- col_names
```
Finally convert the matrix to a tibble
```{r}
T01 <- as_tibble(mat)
rm(text, col_names, mat)
```
Convert string "NA" to NA value. We need 'real' NA values, so we can filter
our dataset later on
```{r}
T01[T01 == "NA"] <- NA
invisible(gc())
```
This is mostly the same routine created earlier for variable `komponentek1di1`
Select only values where ID_T01 has non-NA values (same for columns with .x/.y suffix)
```{r}
t13 <- T01 %>% filter(!is.na(ID_T01)) %>% select(ID_T01, Fehlerhaft)
t11 <- T01 %>% filter(!is.na(ID_T01.x)) %>% select(ID_T01.x, Fehlerhaft.x) %>%
  rename_with(~str_remove(.,'.x'))
t12 <- T01 %>% filter(!is.na(ID_T01.y)) %>% select(ID_T01.y, Fehlerhaft.y) %>%
  rename_with(~str_remove(.,'.y'))
```
After renaming the columns, columns are stacked together 
```{r}
t1clean <- rbind(t11,t12,t13)
t1clean <- t1clean %>% rename(Fehlerhaft.T01 = Fehlerhaft)
```

Have to convert the column to a numeric value. We parsed it as 
a character (with the  scan function)
```{r}
t1clean$Fehlerhaft.T01 <- as.numeric(as.character(t1clean$Fehlerhaft.T01))
```

Einzelteil T02 is pretty much the same routine as Einzelteil T01

Einzelteil T02
```{r}
txt <- str_replace_all(txt_teil2 , "  ", ";")
rm(txt_teil2)
invisible(gc())
lines <- scan(textConnection(txt), what = "character", sep = "\t") 
rm(txt)
text <- str_split(lines, ";")
rm(lines)
invisible(gc())
col_names <- text[[1]]
text <- purrr::map(text[2:length(text)], function(line) {line[-1]})
text <- unlist(text)
mat <- matrix(text, ncol = length(col_names), byrow = TRUE)
colnames(mat) <- col_names
T02 <- as_tibble(mat)
rm(text, col_names, mat)
T02[T02 == "NA"] <- NA
invisible(gc())
```
Difference here is that only entries with .x/.y-suffix are available
```{r}
t21 <- T02 %>% filter(!is.na(ID_T02.x)) %>% select(ID_T02.x, Fehlerhaft.x) %>%
  rename_with(~str_remove(.,'.x'))
t22 <- T02 %>% filter(!is.na(ID_T02.y)) %>% select(ID_T02.y, Fehlerhaft.y) %>%
  rename_with(~str_remove(.,'.y'))
t2clean <- rbind(t21,t22)
t2clean <- t2clean %>% rename(Fehlerhaft.T02 = Fehlerhaft)
t2clean$Fehlerhaft.T02 <- as.numeric(as.character(t2clean$Fehlerhaft.T02))
```
Same procedure: Only take rows where ID_T05.x/TD_T05.y has values. Split and 
stack them
```{r}
t51 <- t5 %>% filter(!is.na(ID_T05.x)) %>% select(ID_T05.x, Fehlerhaft.x) %>%
  rename_with(~str_remove(.,'.x'))
t52 <- t5 %>% filter(!is.na(ID_T05.y)) %>% select(ID_T05.y, Fehlerhaft.y) %>%
  rename_with(~str_remove(.,'.y'))
t5clean <- rbind(t51, t52)
t5clean <- t5clean %>% rename(Fehlerhaft.T5 = Fehlerhaft)
```
Load and rename.
```{r}
t6clean <- t6 %>% select(ID_T06, Fehlerhaft) %>% rename(Fehlerhaft.T6 = Fehlerhaft)
```
Merge all Einzelteil to the kompo_date_motor table.
```{r}
merged <- kompo_date_motor %>% left_join(t5clean, by=c("ID_T5"= "ID_T05"))
merged <- merged %>% left_join(t6clean, by=c("ID_T6" = "ID_T06"))
merged <- merged %>% left_join(t1clean, by=c("ID_T1" = "ID_T01"))
merged <- merged %>% left_join(t2clean, by=c("ID_T2" = "ID_T02"))
invisible(gc())
```
## Creation of the final data set
Create a vector that contains all columns to sum up later on
```{r}
sumcols = c("Fehlerhaft.T01", "Fehlerhaft.T02", "Fehlerhaft.T5", "Fehlerhaft.T6",
            "Fehlerhaft.Motor")
```
All "FehlerhaftXXX" columns in the sumcols are added. Needed are only faulty vehicles with their ID for further analysis.
```{r}
defmotor <- merged %>% mutate(Fehlerhaft=rowSums(merged[,sumcols]) > 0) %>%
  select(ID_Fahrzeug, Fehlerhaft)
```
The resulting vehicles are then matched with register data to know where each of the faulty vehicles are located.
```{r}
defekt <- defmotor %>% inner_join(zl, by=c("ID_Fahrzeug"="IDNummer"))
```

Create a function to calculate distance between municipalities and Berlin
```{r}
distance_calculation <- function(long, lat, berlin_long = 13.40495, berlin_lat = 52.52000){
  R = 6378.137; ##/ Radius of earth in KM
  dLat = lat * pi / 180 - berlin_lat * pi / 180;
  dLon = long * pi / 180 - berlin_long * pi / 180;
  a = sin(dLat/2) * sin(dLat/2) + cos(berlin_lat * pi / 180) * cos(lat * pi / 180) *
    sin(dLon/2) * sin(dLon/2);
  c = 2 * atan2(sqrt(a), sqrt(1-a));
  d = R * c;
  return(d)
}
```
Loading in geo data and select only municipalities in radius of 80km from Berlin
```{r}
gemeinde_in_80km <- geo_daten_gemeinden %>%
  mutate(Distance = distance_calculation(Laengengrad, Breitengrad))%>%
  select(Gemeinden = Gemeinde, Distance)%>%
  filter(Distance <= 80)
```
Join this table with the faulty cars table. The final dataset now shows the filtered cars and where they are registered, while only looking at municipalities maximum 80km away from Berlin
```{r message}
berlin_all <- defekt %>% inner_join(gemeinde_in_80km, by="Gemeinden") %>%
  select(ID_Fahrzeug, Fehlerhaft, Gemeinden)
```

## Evaluation
The final resulting data set contains only vehicles of type 11 with engines of type K1DI1 which were produced from the production period from 21.09.2010 to 04.09.2012 and where the engine or one of its parts is faulty or not faulty at all.
After this the vehicles are matched with the vehicle register data from each municipality to create a recall plan, first only for vehicles in radius 80km from Berlin, but scalable to higher radius.

## Result
```{r message=TRUE}
head(berlin_all)
```